---
title: "FARS Functions"
author: "Peter Ho"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction:

US National Highway Trac Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suered in motor vechicle trac crashes.

## Main Functions:
### fars_summarize_years (years)
This function shows the summary of FARS info (data frame). Count the accidents per month and year.

```{r}
library(pho)
setwd("C:/Users/peterh/Documents/pho/extdata")
fars_summarize_years(2013)
```

### fars_map_state (years)
This function plots the State map with FARS data of a specific year.  If no data to plot, a message and NULL will return.

```{r, fig.show='hold'}
library(maps)
setwd("C:/Users/peterh/Documents/pho/extdata")
fars_map_state(48,2013)
```

## Other Functions:

### make_filename (year)
This function will make a filename based on the input year, which requires a numerical input.

### fars_read_years (years)
This function will take a list of years as input and read the corresponding FARS files of those years.

### fars_read (filename)
This function read FARS data (Fatality Analysis Reporting System) from a CSV file and returns a tibble.  If the path or file is incorrect, the fuction will stop with an error.



